Propositions as Sessions, Mechanically

### 2015-04-11 paper/formalisation.tex
Added tilde to tactics in extract_bnd Ltac script.

@@

\begin{figure}
\begin{coq}
Ltac extract_bnd x A :=
  match goal with
    | [H: Permutation (_++x~A) ?F |- _] =>
      let BNDS := fresh "BNDS" in
      forwards~ BNDS: Perm_binds x A H
      ; analyze_binds_uniq BNDS
      ; try (by applys~ uniq_perm H)
      ; try (match goal with
               | [H: binds x A ?E |- _] =>
                 let E1 := fresh "E1" in
                 let E2 := fresh "E2" in
                 let EQ := fresh "EQ" in
                 apply binds_env_split in H
                 ; inversion_clear H as (E1 & E2 & EQ)
                 ; substs~; des_reqs
             end)
  end.
\end{coq}
\caption{Tactic finds binding in permutation RHS}
\label{fig:extract}
\end{figure}

>>>>

\input{extract}

@@
